Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-03-10 reply_to_reviews.R1.Rmd

3. We see how "reverse the SGPV" might have been confusing. We did not mean to imply to reverse the null and alternative. We now just say that we plot 1-SGPV (which is what we incorrectly tried to express with "reverse").

4. The issue of the SGPV needing a 'correction' by setting it to 0.5 is not related to the fact that large *p*-values are not evidence for the null. The *p*-value is behaving as it is intended to, without any correction. A high *p*-value is not a 'misleading result' - although it can be misinterpreted (which is exactly what we try to prevent with our work on equivalence testing). We therefore did not incorporate this point.

5. In line with comments by reviewer 1, we removed statements about SGPV not being inferential, thereby solving the issue reviewer 2 raised.

@@

6. In line with major point 8, we added information that asymmetric confidence intervals around a correlation are symmetric when Fisher z-transformed. This is just an example of what Blume et al (2018) refer to when they write "The magnitude of an inconclusive second-generation *p*-value can vary slightly when the effect size scale is transformed. However definitive findings, i.e. a *p*-value of 0 or 1 are *not* affected by the scale changes." We believe this section, although the most detailed, is interesting, even only for more expert readers (indeed, Reviewer 1 notes that "The asymmetric CI case is very interesting"). We have made our point less general, now only talking about correlations, by changing the title of this section into "The relation between equivalence tests and SGPV for asymmetrical confidence intervals around correlations". The reviewer is correct confidence intervals can be created in many difference ways (e.g., with holes in the middle), but for this paper, we just focus on one specific case now, which we believe might be closest to what researchers would use in real life, the confidence interval around a correlation.

7. We agree that using TOST for small samples (e.g., N = 4) will not be useful. Indeed, an a-priori power analysis for equivalence tests would prevent anyone from planning such a study, since the result will be that such a study has 0 power - the CI will never fit withing the equivalence bounds.  It is a well-known fact that the TOST can have 0 power (and indeed, this is one of the main issues in the Perlman and Wu (1999) paper the reviewer cited). As explained in Lakens (2017): "It is important to take statistical power into account when determining the equivalence bounds because, in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds)." We agree with the reviewer it is not interesting to do a test if you have 0 power. People should design informative experiments by doing an a-priori power analysis. Any problem in this respect is not a problem with equivalence tests, but a problem with designing a bad study. The paper already contained a section explaining this ("This happens because the we are examining a scenario where the 90% CI is so wide that it never falls completely within the two equivalence bounds. As Lakens (2017) notes: “in small samples (where CIs are wide), a study might have no statistical power (i.e., the CI will always be so wide that it is necessarily wider than the equivalence bounds).” None of the *p*-values based on the TOST procedure are below 0.05, and thus, in the long run we have 0% power").

Note that the exact same issue applies to the SGPV. It is also possible to have 0 power for the SGPV - so we do not understand why the reviewer is so surprised about this. The question "Why use the TOST test then?" equally applies to "Why use the SGPV then?" if you, from the outset, know that the 'small sample correction' will lead to a SGPV of 0.5. Note that, following Reviewer 1's caution in using words ike 'always', we have added a comment about the overlap between the 3 points of TOST and SGPV where we say: "Two other points always have to overlap." which we now follow with: "Note that when sample sizes are small or equivalence bounds are narrow, small *p*-values for the TOST or a SGPV = 1 might not be observed in practice if too few observations are collected."

@@

8. We do not see how setting the SGPV to 0.5 'shrinks' an estimate to some value. Regardless of how correction factors are applied in statistics, we are trying to educate our readers about what the 'small sample correction' does. We believe our readers will associate 'correction' with 'correcting', and want to explain that the SGPV is not set to a 'correct' value. We are not talking about statistical terms here - we are warning the reader to not interpret 'correction' in terms of normal language use. This is similar to warning readers that 'significant' does not have the normal language connotation of 'important'. We have therefore kept our original sentence.

As a final comment, although not explicitly listed as a major point of minor point, we are happy to respond to the reviewers' suggestion that Perlman and Wu (1999) call for an "outright ban of TOST". The best summary of this discussion (of which Perlman & Wu is one contribution) can be found in Meyners (2012), which we cited. The discussion has different arguments, and Meyners draws the conclusion that there is no universially preferred approach. The power benefits of alternative approaches are typically modest, or only noticeable in situations where all alternatives are underpowered. The power issue is not that important - the main discussion is about whether equivalence tests should have a bounded rejection region, like TOST, or an unbounded rejection region. It might be useful to note that TOST and SGPV are similar in this respect - both have bounded rejection regions, and if the reviewer agrees with Perlman and Wu (1999) in the criticism against TOST, the same criticism applies to the SGPV. If the reviewer reads Perlman and Wu (1999) as an argument to ban TOST, it is at the same time an argument to ban the SGPV. We agree with Meyners, who writes: "The debate has been quite heated in times; this section intends to give a brief overview of the debate. We would like to emphasize again that the differences between the approaches are minor and to a large extent of academic interest only, as is this debate." and concludes: "To summarize, there is no right or wrong in most of the arguments; the two opposing parties rather apply different criteria to select the most appropriate test, one group focusing rather on mathematical/statistical criteria, the other one more on interpretability and reasonability." We have added a reference to this discussion for the interested reader, and added "For an excellent discussion of the strengths and weaknesses of different frequentist equivalence tests, including alternatives to the TOST procedure, see Meyners, 2012."

\newpage
# References

### 2019-03-10 reply_to_reviews.R1.tex

\linenumbers

\authornote{

Correspondence concerning this article should be addressed to Daniël
Lakens, Den Dolech 1, IPO 1.33, 5600 MB, Eindhoven, The Netherlands.
E-mail:
\href{mailto:D.Lakens@tue.nl}{\nolinkurl{D.Lakens@tue.nl}}}

\abstract{
We respond to all the comments on our submission that were raised by the
two reviewers, as well as the comments you highlighted as editor. We
would like to thank you and reviewers for suggestions for improvements,
which we believe made our main argument much clearer, focussed, and
formally correct. We feel we were able to accomodate all suggestions,
and we hope you think our submission is ready to be accepted for
publication in Meta-Psychology.

@@

  about the relationship between TOST \emph{p}-values and SGPV in this
  article are not dependent upon any specific example} into \enquote{Our
  conclusions about the relationship between TOST \emph{p}-values and
  SGPV hold for second generation \emph{p}-values calculated from
  confidence intervals, and assuming data is sampled from a bivariate
  normal distribution}. We mainly intended to refer to our conclusion
  that: \enquote{When confidence intervals are symmetric we can think of
  the SGPV as a straight line that is directly related to the
  \emph{p}-value from an equivalence test for three values} namely
  \emph{p} = 0.5 for TOST when the SGPV will be 0.5, and the

@@

  mean where the SGPV is 1). We have now made it clearer that when we
  talk about \enquote{correspondence between TOST \emph{p}-values and
  the SGPV}, we mean that there is a direct relation between three
  points. We have added the explanation: \enquote{When we discuss the
  relationship between the \emph{p}-values from TOST and the SGPV, we
  focus on their correspondence at three values, namely where the TOST
  \emph{p} = 0.025 and SGPV is 1, where the TOST \emph{p} = 0.5 and SGPV
  = 0.5, and where the TOST \emph{p} = 0.975 and SGPV = 1. These three
  values are important for the SGPV because they indicate the values at
  which the SGPV indicates the data should be interpreted as compatible
  with the null hypothesis (SGPV = 1), or with the alternative
  hypothesis (SGPV = 0), or when the data are strictly inconclusive
  (SGPV = 0.5).}

@@

  We now just directly say what we originally meant, and no longer use
  the word \enquote{unrelated}. For example, \enquote{There are three
  situations where \emph{p}-values for TOST differentiate between
  observed results, while the SGPV does not differentiate} and
  \enquote{Where the SGPV is 1 as long as the confidence interval falls

@@

  completely within the equivalence bounds, the \emph{p}-value for the
  TOST continues to differentiate between results as a function of how
  far the confidence interval lies within the equivalence bounds} and
  similarly \enquote{A third situation in which the SGPV remains stable
  across a range of observed effects, while the TOST \emph{p}-value
  continues to differentiate, is whenever the CI is wider than the
  equivalence range, and the CI overlaps with the upper \emph{and} lower
  equivalence bound}. We have removed the word \enquote{unrelated}
  throughout the manuscript.

@@

  training we lack, that allows you to point out whenever we make
  formally incorrect statements. This is exactly why we submit our work
  for peer review - to be able to improve it based on feedback from
  experts. We now preface the sentence with \enquote{As long as data are
  sampled from a bivariate normal distribution,}. We follow your
  recommendation throughout to not generalize beyond the scenarios we
  study. In the second paragraph of the manuscript we now clearly state:
  \enquote{We limit our analysis to continuous data sampled from a
  bivariate normal distribution.} See also point 5 below.

@@

  since the SGPV and \emph{p}-value for the TOST procedure are always
  directly related at these values.} should no longer be confusing. To
  make the sentence clearer, we have changed \enquote{these values} into
  \enquote{at the values \emph{p} = 0.025 and \emph{p} = 0.975} It
  should now be clear the sections are not contradictory - TOST
  differentiates below \emph{p} \textless{} 0.025, when the SGPV is 1
  for all \emph{p} \textless{} 0.025.

@@

  sentence to read: \enquote{Although a SGPV of 1 or 0 can be directly
  interpreted, a SGPV between 0 and 1 is not interpretable as
  \enquote{compatibility with the null hypothesis} under the assumption
  of a bivariate normal distribution, and the generalizability of this
  statement needs to be examined beyond normal bivariate distributions.}

@@

  be interpreted to future researchers, and we do not make any
  statements about whether such values are descriptive or inferential.
\end{enumerate}

Based on your recommendations, we have limited our conclusions to the
specific cases we have examined, and noted the possibility for future
research to examine a wider set of assumptions. An additional change not
mentioned above is that we renamed the section on asymmetric confidence
intervals to the more specific \enquote{The relation between equivalence
tests and SGPV for asymmetrical confidence intervals around
correlations} instead of the more general \enquote{The relation between
equivalence tests and SGPV when confidence intervals are not
symmetrical}. We appreciate the very positive evaluation of our
manuscript, but even more so the criticism which allowed us to improve
the manuscript.

@@

\section{Reply to Reviewer 2}\label{reply-to-reviewer-2}

Before listing major points, the reviewer raises the point that we
compare SGPV with \emph{p}-values from TOST throughout our paper, and in
all figures, but then at the end, in page 20, we wrote:

@@

\enquote{Equivalence tests combined with null-hypothesis significance
tests also allow researchers to conclude an effect is significant and
equivalent (i.e., statistically different from zero, but also too small
to be considered meaningful). Thus, the SGPV is used to classify results
into one of three possible categories (with the data falling inside or
outside the equivalence range, or being inconclusive), while equivalence
tests combined with null-hypothesis tests classify results into four
possible categories.}

The reviewer says that \enquote{the authors suddenly switch the premise;
now the SGPV should be replaced by two \emph{p}-values, one from an
equivalence test and one from a NHST}. However, we do not suggest to
replace the SGPV with an equivalence test and a NHST at all. In our
manuscript, we already pointed out how the SGPV is basically the same as
an equivalence test and a minimum effect test (on page 7), and we have
expanded this text to clarify that a minimum effects test and TOST are
complementary:

\enquote{The third point where the SGPV and the \emph{p}-value from the
TOST procedure should overlap is where the 95\% CI falls completely
outside of the equivalence range, but one endpoint of the confidence
interval is equal to the equivalence bound (see situation C in Figure
3), when the \emph{p}-value will always be 0.975. Note that this
situation is in essence a minimum-effect test (Murphy, Myors, \& Wolach,
2014). The goal of a minimum-effect is not just to reject a difference
of zero, but to reject the smallest effect size of interest (i.e., the
equivalence bounds). An equivalence test and minimum effect test against
the same equivalence bound are complementary, and when a TOST
\emph{p}-value is larger than 0.975, the \emph{p}-value for the minimum
effect test is smaller than 0.05 (and therefore the minimum effect test
provides no additional information that can not be derived from the
\emph{p}-value from the equivalence test). The SGPV summarizes the
information from an equivalence test (and the complementary
minimum-effect test).}

The overlap of the TOST \emph{p}-value at 0.975 when SGPV = 0 gives away
that the equivalence test can be interpreted as a minimum effect test
against the equivalence bound. When the TOST \emph{p}-value is 0.975,
the 95\% CI touches either the upper or lower equivalence bound, and
fall completely outside of the equivalence range. This is mathematically
identical to a statistically significant minimum effect test at \emph{p}
\textless{} 0.05. We clearly should have made this more explicit, and
hope the additional text clarifies the statistical relationship between
TOST, a minimum effect test, and the SGPV

@@

\enquote{Some researchers might be interested in combining an
equivalence tests with a null-hypothesis significance test. This allows
a researcher to ask whether there is an effect that is statistically
different from zero, and whether effect sizes that are considered
meaningful can be rejected. Equivalence tests combined with
null-hypothesis tests classify results into four possible categories,
and for example allow researchers to conclude an effect is significant
and equivalent (i.e., statistically different from zero, but also too
small to be considered meaningful, see (Lakens et al., 2018)).}

We hope this makes it clear we are not pulling a bait and switch. The
SGPV is strongly related to an equivalence test (or it's complement, a
minimum effect test). Describing the relation between the SGPV and TOST
is our main contribution. We just wanted to mention that researchers
might want to combine an equivalence test with a NHST, because in the
literature, this is a question we see many psychologists ask when they
use TOST.

We will now discuss the major points in turn.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  In line with the comments by reviewer 1, in the second paragraph of
  the manuscript we now clearly state: \enquote{We limit our analysis to
  continuous data sampled from a bivariate normal distribution.} and
  \enquote{Our conclusions about the relationship between TOST
  \emph{p}-values and SGPV hold for second generation \emph{p}-values
  calculated from confidence intervals, and assuming data is sampled
  from a bivariate normal distribution.}. After all, \emph{p}-values and
  confidence are directly related, but Bayesian credible intervals would
  not necessarily be, depending on the prior. Blume et al (2018) limit
  their examples to confidence intervals, but explicitly acknowledge
  other possibilities (such as Bayesian intervals). We look forward to
  future papers that illustrate the SGPV with other interval estimates
  and are happy to add the limitation to continuous normally distributed
  data in our article.
\item
  The reviewer notes that the correspondence only holds when SE's are
  small compared to the width of the equivalence range. The
  correspondence we refer to is not in the shape of the curve (which
  clearly differs across Figures 2, 6, and 9). We clearly state that:
  \enquote{When confidence intervals are symmetric we can think of the
  SGPV as a straight line that is directly related to the \emph{p}-value
  from an equivalence test for three values.} This correspondence is not
  dependent upon the SE's. It will always hold for CI based on bivariate
  continuous normally distributed data. The reviewer says that
  \enquote{The paper does not provide theoretical justification for this
  connection nor any proofs.} We do not think proof is needed (the
  \enquote{proof} is that the SGPV and the TOST both use the same
  confidence interval) and we believe the explanation in the paper of
  why this overlap must be so is very clear. A confidence interval and a
  \emph{p}-value are directly related. The TOST procedure is a test
  using the confidence interval, and the SGPV (now that we clearly
  limited our discussion to a SGPV based on a confidence interval
  calculated from continuous normal data) compared against the same
  equivalence bounds will be related as we describe. But we believe our
  article might not have been clear enough about that we limit our
  discussion about the correspondence of the curves to these 3 points.
  Indeed, in some figures, the curves are less similar (e.g., Figure 6,
  9, 13). Nevertheless, in these graphs, we still have the
  correspondence between these 3 points (or at least the 2 points if the
  CI is too wide compared to the equivalence bounds to ever observe a
  \emph{p} = 0.025). To make it clearer that we talk about the overlap
  in these 3 critical points, we have added:
\end{enumerate}

@@

\enquote{When we discuss the relationship between the \emph{p}-values
from TOST and the SGPV, we focus on their correspondence at three
values, namely where the TOST \emph{p} = 0.025 and SGPV is 1, where the
TOST \emph{p} = 0.5 and SGPV = 0.5, and where the TOST \emph{p} = 0.975
and SGPV = 1. These three values are important for the SGPV because they
indicate the values at which the SGPV indicates the data should be
interpreted as compatible with the null hypothesis (SGPV = 1), or with
the alternative hypothesis (SGPV = 0), or when the data are strictly
inconclusive (SGPV = 0.5). These three points of overlap are indicated
by the horizontal dotted lines in Figure 2.}

We believe this satisfactorily addresses the point by the reviewer that
\enquote{Because of this lack of discussion, the reader can easily miss
that the close correspondence only occurs when the sample size is large
enough that the standard error is very small relative to the width of
the equivalence zone.} Indeed, the correspondence between the TOST and
SGPV at these 3 points should be obvious to anyone who understands the
relationship between a \emph{p}-value and a confidence interval, so we
do not provide any further proof, but we hope that clarifying we talk
about the correspondence of these 3 points, and not the entire curve, is
sufficient to address point 2. We have also changed the figures, making
the SGPV a solid line, to make the relationship more clearly visible
compared to the previous dotted curve.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  We are aware of the Beger and Hsu (1996) article. But if the reviewer
  reads more closely, it should be clear that we never say the TOST is
  UMP. We say that TOST is a test procedure that aims to control error
  rates - our use of the term \enquote{Neyman-Pearson perspective}
  refers to the classic difference between significance tests (Fisher)
  and hypothesis tests (Neyman-Pearson). We do not imply that any test
  that fixes an error rate is a NP test. Because many psychologists are
  not trained in the difference between a Fisherian approach and a
  Neyman Pearson approach to the use of \emph{p}-values, we are simply
  adding a \enquote{Neyman-Pearson} approach in the text to explain that
  \enquote{From a Neyman-Pearson perspective on statistical inferences
  the main conclusion is based on whether or not \(p < \alpha\), and
  thus an equivalence test and SGPV can be performed by simply checking
  whether the confidence interval falls within the equivalence range,
  just as a null-hypothesis test can be performed by checking whether
  the confidence interval contains zero or not.} We believe this is a
  correct use of the term \enquote{Neyman-Pearson perspective on
  statistical inferences}.
\item
  We tried to find the passage the reviewer refers to when he writes
  \enquote{In light of this, the assertion without proof that classical
  \emph{p}-values provide more or better assessments of the
  \enquote{evidence} appear out of place.} but we could not. We do not
  use the word \enquote{evidence} in the text (because neither the
  \emph{p}-value from TOST nor the SGPV are measures of
  \enquote{evidence} - we fully agree with Bume et al., 2018, in this
  respect). We also do not say the \emph{p}-value is \enquote{naturally
  informative}. Indeed, related to point 3 above, we tried to be
  consistent in interpreting the TOST procedure from a Neyman-Pearson
  perspective, and focus on error control. So we regrettably do not know
  how to incorporate this point.
\item
  We fully agree with the reviewer on point 5 that \enquote{The maximum
  Type I Error rate for the SGPV over the null interval is 5\%, exactly
  like the TOST test.} Indeed, given the direct overlap between the TOST
  \emph{p}-value and the SGPV at \emph{p} = 0.025 and 0.0975 and SGPV of
  1 and 0, any error rates (when concluding support for the null or
  alternative when the SGPV is either 1 or 0) must be identical. This is
  why we were so surprised when Blume et al (2018) write \enquote{They
  control the Type I error naturally, forcing it to zero as the sample
  size grows. This, in turn, offsets Type I Error inflation that results
  from multiple comparisons or multiple examinations of accumulating
  data. Findings identified by second-generation \emph{p}-values are
  less likely to be false discoveries than findings identified by
  classical \emph{p}-values. Consequently, second-generation
  \emph{p}-values do not require ad-hoc adjustments to provide strict
  error control and this improves power in studies with massive multiple
  comparisons.} Clearly, it can not both be true that the error rate of
  SGPV and TOST is identical, TOST requires adjusting for multiple
  comparisons, but the SGPV does not.
\end{enumerate}

@@

The editor asks us to better substantiate the frequency claims for the
comparison of TOST and SGPV, but since the SGPV and TOST \emph{p}-value
are directly related (a TOST \emph{p} \textless{} 0.025 = a SGPV of 1)
we do not think any additional substantiation is possible, especially
since the reviewer agrees that (as long as confidence intervals are used
to calculate the SGPV, which we now clearly limit our conclusions to)
\enquote{The maximum Type I Error rate for the SGPV over the null
interval is 5\%, exactly like the TOST test}.

Nevertheless, we agree this discussion was a bit too extensive. Given my
own fondness of error control in statistical inferences, I get worried
if researchers suggest we can ignore it, especially when making multiple
comparisons. Imagine people start to use the SGPV instead of the TOST
procedure whenever they perform 20 tests, and then argue they do not
need to correct for multiple comparisons - I think we can all agree this
is undesireable, given that we are trying to fix the replicability
crisis in psychology! We have reduced the two paragraphs to one
hopefully clear statement about the need to control error rates, also
when using the SGPV. We hope this addresses the concerns by the editor
as well as the reviewer, while still making an important point in the
literature about the need to control error rates (if one cares about
drawing incorrect conclusions).

\enquote{Blume, D'Agostino McGowan, Dupont, and Greevy (2018) claim that
when using the SGPV}Adjustments for multiple comparisons are obviated"
(p.~15). However, this is not correct. Given the direct relationship
between TOST and SGPV highlighted in this manuscript (where a TOST
\emph{p} = 0.025 equals SGPV = 1, as long as the SGPV is calculated
based on confidence intervals, and assuming data are sampled from a
continuous bivariate normal distribution), not correcting for multiple
comparisons will inflate the probability of concluding the absence of a
meaningful effect based on the SGPV in exactly the same way as it will
for equivalence tests. Whenever statistical tests are interpreted as
support for a hypothesis (e.g., SPGV = 0 or SGPV = 1), it is possible do
so erroneously, and if researchers want to control error rates, they
need to correct for multiple comparisons."

@@

Minor Concerns:

### 2019-03-10 reply_to_reviews.R1.tex

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  We added \enquote{,or more extreme data,}
\item
  This text was deleted (see major point 5 above)
\item
  We see how \enquote{reverse the SGPV} might have been confusing. We
  did not mean to imply to reverse the null and alternative. We now just
  say that we plot 1-SGPV (which is what we incorrectly tried to express
  with \enquote{reverse}).
\item
  The issue of the SGPV needing a \enquote{correction} by setting it to
  0.5 is not related to the fact that large \emph{p}-values are not
  evidence for the null. The \emph{p}-value is behaving as it is
  intended to, without any correction. A high \emph{p}-value is not a
  \enquote{misleading result} - although it can be misinterpreted (which
  is exactly what we try to prevent with our work on equivalence
  testing). We therefore did not incorporate this point.
\item
  In line with comments by reviewer 1, we removed statements about SGPV
  not being inferential, thereby solving the issue reviewer 2 raised.
\item
  In line with major point 8, we added information that asymmetric
  confidence intervals around a correlation are symmetric when Fisher
  z-transformed. This is just an example of what Blume et al (2018)
  refer to when they write \enquote{The magnitude of an inconclusive
  second-generation \emph{p}-value can vary slightly when the effect
  size scale is transformed. However definitive findings, i.e.~a
  \emph{p}-value of 0 or 1 are \emph{not} affected by the scale
  changes.} We believe this section, although the most detailed, is
  interesting, even only for more expert readers (indeed, Reviewer 1
  notes that \enquote{The asymmetric CI case is very interesting}). We
  have made our point less general, now only talking about correlations,
  by changing the title of this section into \enquote{The relation
  between equivalence tests and SGPV for asymmetrical confidence
  intervals around correlations}. The reviewer is correct confidence
  intervals can be created in many difference ways (e.g., with holes in
  the middle), but for this paper, we just focus on one specific case
  now, which we believe might be closest to what researchers would use
  in real life, the confidence interval around a correlation.
\item
  We agree that using TOST for small samples (e.g., N = 4) will not be
  useful. Indeed, an a-priori power analysis for equivalence tests would
  prevent anyone from planning such a study, since the result will be
  that such a study has 0 power - the CI will never fit withing the
  equivalence bounds. It is a well-known fact that the TOST can have 0
  power (and indeed, this is one of the main issues in the Perlman and
  Wu (1999) paper the reviewer cited). As explained in Lakens (2017):
  \enquote{It is important to take statistical power into account when
  determining the equivalence bounds because, in small samples (where
  CIs are wide), a study might have no statistical power (i.e., the CI
  will always be so wide that it is necessarily wider than the
  equivalence bounds).} We agree with the reviewer it is not interesting
  to do a test if you have 0 power. People should design informative
  experiments by doing an a-priori power analysis. Any problem in this
  respect is not a problem with equivalence tests, but a problem with
  designing a bad study. The paper already contained a section
  explaining this (\enquote{This happens because the we are examining a
  scenario where the 90\% CI is so wide that it never falls completely
  within the two equivalence bounds. As Lakens (2017) notes: \enquote{in
  small samples (where CIs are wide), a study might have no statistical
  power (i.e., the CI will always be so wide that it is necessarily
  wider than the equivalence bounds).} None of the \emph{p}-values based
  on the TOST procedure are below 0.05, and thus, in the long run we
  have 0\% power}).
\end{enumerate}

Note that the exact same issue applies to the SGPV. It is also possible
to have 0 power for the SGPV - so we do not understand why the reviewer
is so surprised about this. The question \enquote{Why use the TOST test
then?} equally applies to \enquote{Why use the SGPV then?} if you, from
the outset, know that the \enquote{small sample correction} will lead to
a SGPV of 0.5. Note that, following Reviewer 1's caution in using words
ike \enquote{always}, we have added a comment about the overlap between
the 3 points of TOST and SGPV where we say: \enquote{Two other points
always have to overlap.} which we now follow with: \enquote{Note that
when sample sizes are small or equivalence bounds are narrow, small
\emph{p}-values for the TOST or a SGPV = 1 might not be observed in
practice if too few observations are collected.}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{7}
\tightlist
\item
  We do not see how setting the SGPV to 0.5 \enquote{shrinks} an
  estimate to some value. Regardless of how correction factors are
  applied in statistics, we are trying to educate our readers about what
  the \enquote{small sample correction} does. We believe our readers
  will associate \enquote{correction} with \enquote{correcting}, and
  want to explain that the SGPV is not set to a \enquote{correct} value.
  We are not talking about statistical terms here - we are warning the
  reader to not interpret \enquote{correction} in terms of normal
  language use. This is similar to warning readers that
  \enquote{significant} does not have the normal language connotation of
  \enquote{important}. We have therefore kept our original sentence.
\end{enumerate}

As a final comment, although not explicitly listed as a major point of
minor point, we are happy to respond to the reviewers' suggestion that
Perlman and Wu (1999) call for an \enquote{outright ban of TOST}. The
best summary of this discussion (of which Perlman \& Wu is one
contribution) can be found in Meyners (2012), which we cited. The
discussion has different arguments, and Meyners draws the conclusion
that there is no universially preferred approach. The power benefits of
alternative approaches are typically modest, or only noticeable in
situations where all alternatives are underpowered. The power issue is
not that important - the main discussion is about whether equivalence
tests should have a bounded rejection region, like TOST, or an unbounded
rejection region. It might be useful to note that TOST and SGPV are
similar in this respect - both have bounded rejection regions, and if
the reviewer agrees with Perlman and Wu (1999) in the criticism against
TOST, the same criticism applies to the SGPV. If the reviewer reads
Perlman and Wu (1999) as an argument to ban TOST, it is at the same time
an argument to ban the SGPV. We agree with Meyners, who writes:
\enquote{The debate has been quite heated in times; this section intends
to give a brief overview of the debate. We would like to emphasize again
that the differences between the approaches are minor and to a large
extent of academic interest only, as is this debate.} and concludes:
\enquote{To summarize, there is no right or wrong in most of the
arguments; the two opposing parties rather apply different criteria to
select the most appropriate test, one group focusing rather on
mathematical/statistical criteria, the other one more on
interpretability and reasonability.} We have added a reference to this
discussion for the interested reader, and added \enquote{For an
excellent discussion of the strengths and weaknesses of different
frequentist equivalence tests, including alternatives to the TOST
procedure, see Meyners, 2012.}

\newpage

\section{References}\label{references}

@@

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-blume_second-generation_2018}{}
Blume, J. D., D'Agostino McGowan, L., Dupont, W. D., \& Greevy, R. A.
(2018). Second-generation p-values: Improved rigor, reproducibility, \&
transparency in statistical analyses. \emph{PLOS ONE}, \emph{13}(3),
e0188299.
doi:\href{https://doi.org/10.1371/journal.pone.0188299}{10.1371/journal.pone.0188299}

\hypertarget{ref-murphy_statistical_2014}{}
Murphy, K. R., Myors, B., \& Wolach, A. H. (2014). \emph{Statistical
power analysis: A simple and general model for traditional and modern
hypothesis tests} (Fourth edition.). New York: Routledge, Taylor \&
Francis Group.
